Human Factors Influencing Visual Statistical Inference

### 2013-07-24 sociology_paper.tex
Manova test = Wilks used
reference updated

\subsection{Location Effect} \label{sec:location_design} Experiment 9 was designed to collect data to assess the location effect of a actual data plot in a lineup. The data used, documented in \citep{atwood:2013}, measures gene expression of soybean by RNA-seq methods. Two factors were of primary interest: genotype and the interaction between genotype (call them RPA and EV) and iron sufficiency. Three replicates of all but one treatment were included, with the remaining treatment only having two replicates due one replicate being removed to a data quality concern. There are on the order of *** genes examined for significant expression. In large studies such as this there is a valid question whether the data exhibits any structure at all, or if the small $p$-values are simply occurring by chance, from the massive multiple testing. This overall significance is studied by visual inference. Full results are documented in \cite{tengfei:2013}.

@@

*** Why MANOVA rather than ANOVA? Explain this better here.

@@

\subsubsection{Sample of lineup}
\subsubsection{Sample of Null Plots}

\subsubsection{Location Effect}

@@

\begin{table}[hbtp]
\caption{The results obtained by fitting MANOVA Model \eqref{manova}.}
\begin{center}
\begin{tabular}{ccccccccc}
  \hline \hline
 Location & && & \multicolumn{3}{c} {Degrees of Freedom}  & F test \\
 \cline{5-7}
 Effect & DF & Pillai & Approx. F & Numerator& Denumerator &Residual & $p$-value\\
  \hline
  Interaction& 3&1.4783 &0.7772&15&12 & 6 & 0.6821 \\ 
  Genotype &4&1.7796 &1.1221&20&28 & 8 &  0.3824 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:manova}
\end{table}

>>>>

\subsection{Location Effect} \label{sec:location_design} Experiment 9 was designed to collect data to assess the location effect of a actual data plot in a lineup. The data used, documented in \citep{atwood:2013}, measures gene expression of soybean by RNA-seq methods. Two factors were of primary interest: genotype and the interaction between genotype (call them RPA and EV) and iron sufficiency. Three replicates of all but one treatment were included, with the remaining treatment only having two replicates due one replicate being removed to a data quality concern. There are on the order of \dc{***} genes examined for significant expression. In large studies such as this there is a valid question whether the data exhibits any structure at all, or if the small $p$-values are simply occurring by chance, from the massive multiple testing. This overall significance is studied by visual inference. Full results are documented in \citep{atwood:2013}.

@@

\dc{*** Why MANOVA rather than ANOVA? Explain this better here.}

@@

@@

\begin{table}[hbtp]
\caption{The summary of the results obtained by fitting MANOVA Model \eqref{manova} using Wilks test.}
\begin{center}
\begin{tabular}{ccccccccc}
  \hline \hline
 Location & && & \multicolumn{3}{c} {Degrees of Freedom}  & F test \\
 \cline{5-7}
 Effect & DF & Wilks & Approx. F & Numerator& Denumerator &Residual & $p$-value\\
  \hline
  Interaction& 3&0.07986 & 0.592 &15&5.92 & 6 & 0.8082 \\ 
  Genotype & 4&0.01689 & 1.722 & 20&14.22 & 8 & 0.1488 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:manova}
\end{table}
